LAGOS lake depth

### 2020-02-24 figures/02_depth_model.Rmd
create residual density plots

```{r 02_depth_model, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}

dt <- readRDS("../data/01_depth_model/depth_model.rds")
```

```{r 02_depth_model_fitted, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}

>>>>

```{r 02_depth_model_grid_resid, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}

lgus <- read.csv("../data/lagosus_depth_predictors.csv", 
                 stringsAsFactors = FALSE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid)) %>%
  dplyr::select(-lake_maxdepth_m) %>%
  distinct(lagoslakeid, .keep_all = TRUE)
dt   <- readRDS("../data/01_depth_model/depth_grid.rds") %>%
  mutate(lagoslakeid = as.character(lagoslakeid)) %>%
  left_join(lgus, by = "lagoslakeid")

ggplot(data = dt) + 
  geom_density(aes(x = resid, fill = shape_class)) +
  geom_vline(aes(xintercept = 0)) +
  facet_wrap(~ model)

ggplot(data = dt) + 
  geom_density(aes(x = resid, fill = reservoir_class)) +
  geom_vline(aes(xintercept = 0)) +
  facet_wrap(~ model)
```

```{r 02_depth_model_fitted, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
dt <- readRDS("../data/01_depth_model/depth_model.rds")
